Specification of Advanced Types Translation

### 2014-03-06 DOCUMENTATION/AdvancedTypes.tex
Small grammar problems fixed.

\subsubsection{Getting a element from array}

@@

The element access of array can need a shift in indexes. When the domain of 
array is an interval and it is not started from zero, it must adjust the 
indexes shifting the access, because the addressing  of array in intermediate 
representation LLVM starts at 0. To access an element from array the formula is 
$address(e(i1,..,in))  = i1-i1\_start, ... , in-in\_start$. The following rule 
\footnote{The function $TSymbol$ returns the "start", "end" and type of the one 
index.} makes the shift for each index of array. \VGM{TODO: The function TSymbol
returns the "start", "end" and type of the one index.}

@@

\paragraph{Restriction on array:} The translation of direct attribution
 between array expression is not yet supported, for example:

>>>>

\subsubsection{Getting an element from array}

@@

The element access of array can need a shift in indexes. When the domain of 
array is an interval and it is not started from zero, it must adjust the 
indexes shifting the access, because the addressing  of array in intermediate 
representation LLVM starts at 0. To access an element from array the formula is 
$address(e(i1,..,in))  = i1-i1\_start, ... , in-in\_start$. The following rule 
\footnote{The function $TSymbol$ returns the ``start'', ``end'' and type of the one 
index.} makes the shift for each index of array. \VGM{TODO: The function TSymbol
returns the ``start'', ``end'' and type of the one index.}

@@

\paragraph{Restriction on array:} The translation of direct attribution
 between arrays is not yet supported, for example:
